---
title: "Matt Morris '18 HH Project"
author: "Matthew Morris"
date: "2/3/16 "
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` setion of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))


```{r}
Fac0405 = read.csv("~/MattMorris18/HHFindAge/data/04 05 Faculty.csv")
Fac0506 = read.csv("~/MattMorris18/HHFindAge/data/05 06 Faculty.csv")
Fac0607 = read.csv("~/MattMorris18/HHFindAge/data/06 07 Faculty.csv")
Fac0708 = read.csv("~/MattMorris18/HHFindAge/data/07 08 Faculty.csv")
Fac0809 = read.csv("~/MattMorris18/HHFindAge/data/08 09 Faculty.csv")
Fac0910 = read.csv("~/MattMorris18/HHFindAge/data/09 10 Faculty.csv")
Fac1011 = read.csv("~/MattMorris18/HHFindAge/data/10 11 Faculty.csv")
Fac1112 = read.csv("~/MattMorris18/HHFindAge/data/11 12 Faculty.csv")
Fac1213 = read.csv("~/MattMorris18/HHFindAge/data/1213 Faculty.csv")
Fac1314 = read.csv("~/MattMorris18/HHFindAge/data/1314 Faculty.csv")
```

```{r}
Fac0405r = na.omit(Fac0405)
Fac0506r = na.omit(Fac0506)
Fac0607r = na.omit(Fac0607)
Fac0708r = na.omit(Fac0708)
Fac0809r = na.omit(Fac0809)
Fac0910r = na.omit(Fac0910)
Fac1011r = na.omit(Fac1011)
Fac1112r = na.omit(Fac1112)
Fac1213r = na.omit(Fac1213)
Fac1314r = na.omit(Fac1314)
```

```{r}
avgage0405 = round(with(Fac0405r,mean(Age)),digits=1)
avgage0506 = round(with(Fac0506r,mean(Age)),digits=1)
avgage0607 = round(with(Fac0607r,mean(Age)),digits=1)
avgage0708 = round(with(Fac0708r,mean(Age)),digits=1)
avgage0809 = round(with(Fac0809r,mean(Age)),digits=1)
avgage0910 = round(with(Fac0910r,mean(Age)),digits=1)
avgage1011 = round(with(Fac1011r,mean(Age)),digits=1)
avgage1112 = round(with(Fac1112r,mean(Age)),digits=1)
avgage1213 = round(with(Fac1213r,mean(Age)),digits=1)
avgage1314 = round(with(Fac1314r,mean(Age)),digits=1)
avgageovertime = c(avgage0405,avgage0506,avgage0607,avgage0708,avgage0809,avgage0910,avgage1011,avgage1112,avgage1213,avgage1314)
```

My estimated average age for the Williams College Faculty for the last 10 years are as follows:



2004-2005 = 45.1 

2005-2006 = 46 

2006-2007 = 45.7

2007-2008 = 46.5

2008-2009 = 47 

2009-2010 = 48.3 

2010-2011 = 48.7

2011-2012 = 48.7

2012-2013 = 48.2

2013-2014 = 48.1

```{r,fig.height=6,fig.width=8}
barplot(avgageovertime,main="Average Age of Williams Faculty over Past 10 Years",ylab="Age",names.arg=c("2004-2005","2005-2006","2006-2007","2007-2008","2008-2009","2009-2010","2010-2011","2011-2012","2012-2013","2013-2014"),col=terrain.colors(10),las=2,ylim=c(0,50))
```

```{r}
minage0405 = with(Fac0405r,min(Age))
maxage0405 = with(Fac0405r,max(Age))
minage0506 = with(Fac0506r,min(Age))
maxage0506 = with(Fac0506r,max(Age))
minage0607 = with(Fac0607r,min(Age))
maxage0607 = with(Fac0607r,max(Age))
minage0708 = with(Fac0708r,min(Age))
maxage0708 = with(Fac0708r,max(Age))
minage0809 = with(Fac0809r,min(Age))
maxage0809 = with(Fac0809r,max(Age))
minage0910 = with(Fac0910r,min(Age))
maxage0910 = with(Fac0910r,max(Age))
minage1011 = with(Fac1011r,min(Age))
maxage1011 = with(Fac1011r,max(Age))
minage1112 = with(Fac1112r,min(Age))
maxage1112 = with(Fac1112r,max(Age))
minage1213 = with(Fac1213r,min(Age))
maxage1213 = with(Fac1213r,max(Age))
minage1314 = with(Fac1314r,min(Age))
maxage1314 = with(Fac1314r,max(Age))
```

The youngest and oldest faculty member's age and name for the last 10 years are as follows:


Youngest 2004-2005 = \(\Sexpr{minage0405}\), Zafrir Levy, Assistant Professor of Physical Education and Head Coach of Men's and Women's Squash

Oldest 2004-2005 = \(\Sexpr{maxage0405}\), Henry J. Bruton, Visiting Professor of Economics

Youngest 2005-2006 = \(\Sexpr{minage0506}\), Heather N. Harrington, Assistant Project Cataloger

Oldest 2005-2006 = \(\Sexpr{maxage0506}\), Henry J. Bruton, Visting Professor of Economics

Youngest 2006-2007 = \(\Sexpr{minage0607}\), Robert Michelin, Visting Lecturer in Music and Director of Zambezi

Oldest 2006-2007 = \(\Sexpr{maxage0607}\), Henry J. Bruton Visting Professor of Economics

Youngest 2007-2008 = \(\Sexpr{minage0708}\), Heather Harrington, Collections Archivist and Marshall K. Creighton, Lecturer in Physical Education

Oldest 2007-2008 = \(\Sexpr{maxage0708}\), Henry J. Bruton, Visting Professor of Economics

Youngest 2008-2009 = \(\Sexpr{minage0809}\), Binyavanga Wainaina, Sterling Brown '22 Visiting Professor of Africana Studies, First Semester

Oldest 2008-2009 = \(\Sexpr{maxage0809}\), Henry J. Bruton, Visting Professor of Economics

Youngest 2009-2010 = \(\Sexpr{minage0910}\), David A. Chalifoux, Library Shelving Facility Supervisor

Oldest 2009-2010 = \(\Sexpr{maxage0910}\), Henry J. Bruton, Visting Professor of Economics

Youngest 2010-2011 = \(\Sexpr{minage1011}\), Daniel Greenberg, Lecturer of Physical Education and Head Men's Tennis Coach

Oldest 2010-2011 = \(\Sexpr{maxage1011}\), Henry J. Bruton, Visting Professor of Economics

Youngest 2011-2012 = \(\Sexpr{minage1112}\), Daniel Greenberg, Assistant Professor of Physical Education and Head Men's Tennis Coach

Oldest 2011-2012 = \(\Sexpr{maxage1112}\), Henry J. Bruton, Visting Professor of Economics

Youngest 2012-2013 = \(\Sexpr{minage1213}\), Qing(Wendy) Wang, Assistant Professor of Statistics

Oldest 2012-2013 = \(\Sexpr{maxage1213}\), Henry J. Bruton, Visting Professor of Economics

Youngest 2013-2014 = \(\Sexpr{minage1314}\), Sarah A. Mirseyedi, Visiting Lecturer in Art

Oldest 2013-2014 = \(\Sexpr{maxage1314}\), Charles B. Dew, Ephraim Williams Professor of American History

###How the Number of Faculty have changed over time? Disclaimer about library

```{r}
numberoffaculty = c(405,404,417,409,422,374,378,383,401,418)
bpovertime = barplot(numberoffaculty,names.arg=c("2004-2005","2005-2006","2006-2007","2007-2008","2008-2009","2009-2010","2010-2011","2011-2012","2012-2013","2013-2014"),xlab="Year",ylab="Number of Faculty", main="Number of Faculty Over Time(Disclaimer about Library)",ylim=c(0,500),las=2,col=topo.colors(10))
```

###How has the age distribution of the professors changed over time?

```{r,fig.show='hold'}
hist0405 = with(Fac0405r,hist(Age, main = "Faculty Age of Williams Professors 2004-2005",ylab = "Number of Professors",ylim=c(0,70),xlim=c(15,85),las=2,col=cm.colors(12)))
hist0506 = with(Fac0506r,hist(Age, main = "Faculty Age of Williams Professors 2005-2006",ylab = "Number of Professors",ylim=c(0,70),xlim=c(20,90),las=2,col=cm.colors(12)))
```

```{r,fig.show='hold'}
hist0607 = with(Fac0607r,hist(Age, main = "Faculty Age of Williams Professors 2006-2007",ylab = "Number of Professors",ylim=c(0,70),xlim=c(20,90),las=2,col=cm.colors(12)))
hist0708 = with(Fac0708r,hist(Age, main = "Faculty Age of Williams Professors 2007-2008",ylab = "Number of Professors",ylim=c(0,70),xlim=c(20,90),las=2,col=cm.colors(12)))
```

```{r,fig.show='hold'}
hist0607 = with(Fac0607r,hist(Age, main = "Faculty Age of Williams Professors 2006-2007",ylab = "Number of Professors",ylim=c(0,70),xlim=c(20,90),las=2,col=cm.colors(12)))
hist0708 = with(Fac0708r,hist(Age, main = "Faculty Age of Williams Professors 2007-2008",ylab = "Number of Professors",ylim=c(0,70),xlim=c(20,90),las=2,col=cm.colors(12)))
```

```{r,fig.show='hold'}
hist0809 = with(Fac0809r,hist(Age, main = "Faculty Age of Williams Professors 2008-2009",ylab = "Number of Professors",ylim=c(0,60),xlim=c(20,90),las=2,col=cm.colors(12)))
hist0910 = with(Fac0910r,hist(Age, main = "Faculty Age of Williams Professors 2009-2010",ylab = "Number of Professors",ylim=c(0,70),xlim=c(20,90),las=2,col=cm.colors(12)))
```

```{r}
hist1011 = with(Fac1011r,hist(Age, main = "Faculty Age of Williams Professors 2010-2011",ylab = "Number of Professors",ylim=c(0,70),xlim=c(20,100),las=2,col=cm.colors(12)))
hist1112 = with(Fac1112r,hist(Age, main = "Faculty Age of Williams Professors 2011-2012",ylab = "Number of Professors",ylim=c(0,70),xlim=c(20,100),las=2,col=cm.colors(12)))
```

```{r}
hist1213 = with(Fac1213r,hist(Age, main = "Faculty Age of Williams Professors 2012-2013",ylab = "Number of Professors",ylim=c(0,70),xlim=c(20,100),las=2,col=cm.colors(12)))
hist1314 = with(Fac1314r,hist(Age, main = "Faculty Age of Williams Professors 2013-2014",ylab = "Number of Professors",ylim=c(0,70),xlim=c(20,80),las=2,col=cm.colors(12)))
```

###Average Ages by Department??

```{r}
avgbydept0405 = tapply(Fac0405r$Age,Fac0405r$Department,mean)
avgbydept0506 = tapply(Fac0506r$Age,Fac0506r$Department,mean)
avgbydept0607 = tapply(Fac0607r$Age,Fac0607r$Department,mean)
avgbydept0708 = tapply(Fac0708r$Age,Fac0708r$Department,mean)
avgbydept0809 = tapply(Fac0809r$Age,Fac0809r$Department,mean)
avgbydept0910 = tapply(Fac0910r$Age,Fac0910r$Department,mean)
avgbydept1011 = tapply(Fac1011r$Age,Fac1011r$Department,mean)
avgbydept1112 = tapply(Fac1112r$Age,Fac1112r$Department,mean)
avgbydept1213 = tapply(Fac1213r$Age,Fac1213r$Department,mean)
avgbydept1314 = tapply(Fac1314r$Age,Fac1314r$Department,mean)
```

```{r,fig.show='hold'}
bpd0405 = barplot(avgbydept0405,main="Average Age of Faculty by Department 2004-2005",ylab="Age",las=2,ylim=c(0,70),col=rainbow(42))
bpd0506 = barplot(avgbydept0506,main="Average Age of Faculty by Department 2005-2006",ylab="Age",las=2,ylim=c(0,70),col=rainbow(42))
```

```{r,fig.height=6,fig.width=8}
bpd0607 = barplot(avgbydept0607,main="Average Age of Faculty by Department 2006-2007",ylab="Age",las=2,ylim=c(0,80),col=rainbow(42))
bpd0708 = barplot(avgbydept0708,main="Average Age of Faculty by Department 2007-2008",ylab="Age",las=2,ylim=c(0,80),col=rainbow(42))
```

```{r,fig.show='hold'}
bpd0809 = barplot(avgbydept0809,main="Average Age of Faculty by Department 2008-2009",ylab="Age",las=2,ylim=c(0,80),col=rainbow(42))
bpd0910 = barplot(avgbydept0910,main="Average Age of Faculty by Department 2009-2010",ylab="Age",las=2,ylim=c(0,80),col=rainbow(42))
```

```{r,fig.show='hold'}
bpd1011 = barplot(avgbydept1011,main="Average Age of Faculty by Department 2010-2011",ylab="Age",las=2,ylim=c(0,80),col=rainbow(42))
bpd1112 = barplot(avgbydept1112,main="Average Age of Faculty by Department 2011-2012",ylab="Age",las=2,ylim=c(0,80),col=rainbow(42))
```

```{r,fig.show='hold'}
bpd1213 = barplot(avgbydept1213,main="Average Age of Faculty by Department 2012-2013",ylab="Age",las=2,ylim=c(0,80),col=rainbow(42))
bpd1314 = barplot(avgbydept1314,main="Average Age of Faculty by Department 2013-2014",ylab="Age",las=2,ylim=c(0,80),col=rainbow(42))
```

###How do the ages differ by gender?

```{r}
avgbygender0405 = tapply(Fac0405r$Age,Fac0405r$Gender,mean)
avgbygender0506 = tapply(Fac0506r$Age,Fac0506r$Gender,mean)
avgbygender0607 = tapply(Fac0607r$Age,Fac0607r$Gender,mean)
avgbygender0708 = tapply(Fac0708r$Age,Fac0708r$Gender,mean)
avgbygender0809 = tapply(Fac0809r$Age,Fac0809r$Gender,mean)
avgbygender0910 = tapply(Fac0910r$Age,Fac0910r$Gender,mean)
avgbygender1011 = tapply(Fac1011r$Age,Fac1011r$Gender,mean)
avgbygender1112 = tapply(Fac1112r$Age,Fac1112r$Gender,mean)
avgbygender1213 = tapply(Fac1213r$Age,Fac1213r$Gender,mean)
avgbygender1314 = tapply(Fac1314r$Age,Fac1314r$Gender,mean)
```

```{r,fig.show='hold'}
bpg0405 = barplot(avgbygender0405,main="Average Age of Faculty by Gender 2004-2005",ylab="Age",las=2,ylim=c(0,50),col=rainbow(2))
bpg0506 = barplot(avgbygender0506,main="Average Age of Faculty by Gender 2005-2006",ylab="Age",las=2,ylim=c(0,50),col=rainbow(2))
```

```{r,fig.show='hold'}
bpg0607 = barplot(avgbygender0607,main="Average Age of Faculty by Gender 2006-2007",ylab="Age",las=2,ylim=c(0,50),col=rainbow(2))
bpg0708 = barplot(avgbygender0708,main="Average Age of Faculty by Gender 2007-2008",ylab="Age",las=2,ylim=c(0,50),col=rainbow(2))
```

```{r,fig.show='hold'}
bpg0809 = barplot(avgbygender0809,main="Average Age of Faculty by Gender 2008-2009",ylab="Age",las=2,ylim=c(0,50),col=rainbow(2))
bpg0910 = barplot(avgbygender0910,main="Average Age of Faculty by Gender 2009-2010",ylab="Age",las=2,ylim=c(0,50),col=rainbow(2))
```

```{r,fig.show='hold'}
bpg1011 = barplot(avgbygender1011,main="Average Age of Faculty by Gender 2010-2011",ylab="Age",las=2,ylim=c(0,60),col=rainbow(2))
bpg1112 = barplot(avgbygender1112,main="Average Age of Faculty by Gender 2011-2012",ylab="Age",las=2,ylim=c(0,60),col=rainbow(2))
```

```{r,fig.show='hold'}
bpg1213 = barplot(avgbygender1213,main="Average Age of Faculty by Gender 2012-2013",ylab="Age",las=2,ylim=c(0,60),col=rainbow(2))
bpg1314 = barplot(avgbygender1314,main="Average Age of Faculty by Gender 2013-2014",ylab="Age",las=2,ylim=c(0,60),col=rainbow(2))
```

###Correlation between Age and Year of Terminal Degree.

```{r}
avgagebytermd0405 = tapply(Fac0405r$Age,Fac0405r$Year.of.Terminal,mean)
avgagebytermd0506 = tapply(Fac0506r$Age,Fac0506r$Year.of.Terminal,mean)
avgagebytermd0607 = tapply(Fac0607r$Age,Fac0607r$Year.of.Terminal,mean)
avgagebytermd0708 = tapply(Fac0708r$Age,Fac0708r$Year.of.Terminal,mean)
avgagebytermd0809 = tapply(Fac0809r$Age,Fac0809r$Year.of.Terminal,mean)
avgagebytermd0910 = tapply(Fac0910r$Age,Fac0910r$Year.of.Terminal,mean)
avgagebytermd1011 = tapply(Fac1011r$Age,Fac1011r$Year.of.Terminal,mean)
avgagebytermd1112 = tapply(Fac1112r$Age,Fac1112r$Year.of.Terminal,mean)
avgagebytermd1213 = tapply(Fac1213r$Age,Fac1213r$Year.of.Terminal,mean)
avgagebytermd1314 = tapply(Fac1314r$Age,Fac1314r$Year.of.Terminal,mean)
```

```{r,fig.show='hold'}
bptdage0405 = barplot(avgagebytermd0405,main="Average Age of Faculty by Year of Terminal Degree 2004-2005",ylab="Average Age",las=2,ylim=c(0,100),col=rainbow(48))
bptdage0506 = barplot(avgagebytermd0506,main="Average Age of Faculty by Year of Terminal Degree 2005-2006",ylab="Average Age",las=2,ylim=c(0,100),col=rainbow(48))
```

```{r,fig.show='hold'}
bptdage0607 = barplot(avgagebytermd0607,main="Average Age of Faculty by Year of Terminal Degree 2006-2007",ylab="Average Age",las=2,ylim=c(0,100),col=rainbow(48))
bptdage0708 = barplot(avgagebytermd0708,main="Average Age of Faculty by Year of Terminal Degree 2007-2008",ylab="Average Age",las=2,ylim=c(0,100),col=rainbow(48))
```

```{r,fig.show='hold'}
bptdage0809 = barplot(avgagebytermd0809,main="Average Age of Faculty by Year of Terminal Degree 2008-2009",ylab="Average Age",las=2,ylim=c(0,100),col=rainbow(48))
bptdage0910 = barplot(avgagebytermd0910,main="Average Age of Faculty by Year of Terminal Degree 2009-2010",ylab="Average Age",las=2,ylim=c(0,100),col=rainbow(48))
```

```{r,fig.show='hold'}
bptdage1011 = barplot(avgagebytermd1011,main="Average Age of Faculty by Year of Terminal Degree 2010-2011",ylab="Average Age",las=2,ylim=c(0,100),col=rainbow(48))
bptdage1112 = barplot(avgagebytermd1112,main="Average Age of Faculty by Year of Terminal Degree 2011-2012",ylab="Average Age",las=2,ylim=c(0,100),col=rainbow(48))
```

```{r,fig.show='hold'}
bptdage1213 = barplot(avgagebytermd1213,main="Average Age of Faculty by Year of Terminal Degree 2012-2013",ylab="Average Age",las=2,ylim=c(0,100),col=rainbow(48))
bptdage1314 = barplot(avgagebytermd1314,main="Average Age of Faculty by Year of Terminal Degree 2013-2014",ylab="Average Age",las=2,ylim=c(0,100),col=rainbow(48))
```

###Do certain departments require more time to earn a PhD or Terminal Degree in than others?

```{r}
avgbytermdegdept0405 = tapply(Fac0405r$B.A.to.Terminal,Fac0405r$Department,mean)
avgbytermdegdept0506 = tapply(Fac0506r$B.A.to.Terminal,Fac0506r$Department,mean)
avgbytermdegdept0607 = tapply(Fac0607r$B.A.to.Terminal,Fac0607r$Department,mean)
avgbytermdegdept0708 = tapply(Fac0708r$B.A.to.Terminal,Fac0708r$Department,mean)
avgbytermdegdept0809 = tapply(Fac0809r$B.A.to.Terminal,Fac0809r$Department,mean)
avgbytermdegdept0910 = tapply(Fac0910r$B.A.to.Terminal,Fac0910r$Department,mean)
avgbytermdegdept1011 = tapply(Fac1011r$B.A.to.Terminal,Fac1011r$Department,mean)
avgbytermdegdept1112 = tapply(Fac1112r$B.A.to.Terminal,Fac1112r$Department,mean)
avgbytermdegdept1213 = tapply(Fac1213r$B.A.to.Terminal,Fac1213r$Department,mean)
avgbytermdegdept1314 = tapply(Fac1314r$B.A.to.Terminal,Fac1314r$Department,mean)
```

```{r,fig.show='hold'}
bptd0405 = barplot(avgbytermdegdept0405,main="Average Time Between Bachelers and Terminal Degree by Department 2004-2005",ylab="Age",las=2,ylim=c(0,20),col=rainbow(42))
bptd0506 = barplot(avgbytermdegdept0506,main="Average Time Between Bachelers and Terminal Degree by Department 2005-2006",ylab="Age",las=2,ylim=c(0,20),col=rainbow(42))
```

```{r,fig.show='hold'}
bptd0607 = barplot(avgbytermdegdept0607,main="Average Time Between Bachelers and Terminal Degree by Department 2006-2007",ylab="Age",las=2,ylim=c(0,20),col=rainbow(42))
bptd0708 = barplot(avgbytermdegdept0708,main="Average Time Between Bachelers and Terminal Degree by Department 2007-2008",ylab="Age",las=2,ylim=c(0,20),col=rainbow(42))
```

```{r,fig.show='hold'}
bptd0809 = barplot(avgbytermdegdept0809,main="Average Time Between Bachelers and Terminal Degree by Department 2008-2009",ylab="Age",las=2,ylim=c(0,20),col=rainbow(42))
bptd0910 = barplot(avgbytermdegdept0910,main="Average Time Between Bachelers and Terminal Degree by Department 2009-2010",ylab="Age",las=2,ylim=c(0,20),col=rainbow(42))
```

```{r,fig.show='hold'}
bptd1011 = barplot(avgbytermdegdept1011,main="Average Time Between Bachelers and Terminal Degree by Department 2010-2011",ylab="Age",las=2,ylim=c(0,15),col=rainbow(42))
bptd1112 = barplot(avgbytermdegdept1112,main="Average Time Between Bachelers and Terminal Degree by Department 2011-2012",ylab="Age",las=2,ylim=c(0,20),col=rainbow(42))
```

```{r,fig.show='hold'}
bptd1213 = barplot(avgbytermdegdept1213,main="Average Time Between Bachelers and Terminal Degree by Department 2012-2013",ylab="Age",las=2,ylim=c(0,20),col=rainbow(42))
bptd1314 = barplot(avgbytermdegdept1314,main="Average Time Between Bachelers and Terminal Degree by Department 2013-2014",ylab="Age",las=2,ylim=c(0,15),col=rainbow(42))
```

###Distribution of Ages over the last 10 years with summary stats:

```{r}
boxplotage0405 = with(Fac0405r,boxplot(Age,ylim=c(0,100),xlab="Age",col="sienna",main="Williams Faculty Age Distribution 2004-2005",horizontal=TRUE))
sumage0405 = with(Fac0405r,summary(Age))
sumage0405
```

```{r}
boxplotage0506 = with(Fac0506r,boxplot(Age,ylim=c(0,100),xlab="Age",col="sienna",main="Williams Faculty Age Distribution 2005-2006",horizontal=TRUE))
sumage0506 = with(Fac0506r,summary(Age))
sumage0506
```

```{r}
boxplotage0607 = with(Fac0607r,boxplot(Age,ylim=c(0,100),xlab="Age",col="sienna",main="Williams Faculty Age Distribution 2006-2007",horizontal=TRUE))
sumage0607 = with(Fac0607r,summary(Age))
sumage0607
```

```{r}
boxplotage0708 = with(Fac0708r,boxplot(Age,ylim=c(0,100),xlab="Age",col="sienna",main="Williams Faculty Age Distribution 2007-2008",horizontal=TRUE))
sumage0708 = with(Fac0708r,summary(Age))
sumage0708
```

```{r}
boxplotage0809 = with(Fac0809r,boxplot(Age,ylim=c(0,100),xlab="Age",col="sienna",main="Williams Faculty Age Distribution 2008-2009",horizontal=TRUE))
sumage0809 = with(Fac0809r,summary(Age))
sumage0809
```

```{r}
boxplotage0910 = with(Fac0910r,boxplot(Age,ylim=c(0,100),xlab="Age",col="sienna",main="Williams Faculty Age Distribution 2009-2010",horizontal=TRUE))
sumage0910 = with(Fac0910r,summary(Age))
sumage0910
```

```{r}
boxplotage1011 = with(Fac1011r,boxplot(Age,ylim=c(0,100),xlab="Age",col="sienna",main="Williams Faculty Age Distribution 2010-2011",horizontal=TRUE))
sumage1011 = with(Fac1011r,summary(Age))
sumage1011
```

```{r}
boxplotage1112 = with(Fac1112r,boxplot(Age,ylim=c(0,100),xlab="Age",col="sienna",main="Williams Faculty Age Distribution 2011-2012",horizontal=TRUE))
sumage1112 = with(Fac1112r,summary(Age))
sumage1112
```

```{r}
boxplotage1213 = with(Fac1213r,boxplot(Age,ylim=c(0,100),xlab="Age",col="sienna",main="Williams Faculty Age Distribution 2012-2013",horizontal=TRUE))
sumage1213 = with(Fac1213r,summary(Age))
sumage1213
```

```{r}
boxplotage1314 = with(Fac1314r,boxplot(Age,ylim=c(0,100),xlab="Age",col="sienna",main="Williams Faculty Age Distribution 2013-2014",horizontal=TRUE))
sumage1314 = with(Fac1314r,summary(Age))
sumage1314
```


